Supporting Information: The Regional Effects of Marine Protected Areas

### 2020-04-26 documents/ovando-regional-effects-of-mpas-si.tex
resubmissted version to PNAS (#1)
* version re-submited to PNAS

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Supporting Information: The Regional Effects of Marine Protected Areas},
            pdfauthor={Daniel Ovando,Jennifer E. Caselle,Christopher Costello,Olivier Deschenes,Steven D. Gaines,Ray Hilborn,Owen Liu},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

@@

@@

bookdown & bookdown & 0.13 & 2019-08-21 & CRAN (R 3.6.0)\\

@@

classInt & classInt & 0.4-1 & 2019-08-06 & CRAN (R 3.6.0)\\

@@

@@

crul & crul & 0.8.4 & 2019-08-02 & CRAN (R 3.6.0)\\

@@

data.table & data.table & 1.12.4 & 2019-10-03 & CRAN (R 3.6.1)\\

@@

devtools & devtools & 2.2.0 & 2019-09-07 & CRAN (R 3.6.0)\\
digest & digest & 0.6.21 & 2019-09-20 & CRAN (R 3.6.0)\\

@@

DT & DT & 0.9 & 2019-09-17 & CRAN (R 3.6.1)\\

@@

@@

gdtools & gdtools & 0.2.0 & 2019-09-03 & CRAN (R 3.6.0)\\

@@

geojsonio & geojsonio & 0.7.0 & 2019-04-25 & CRAN (R 3.6.0)\\

@@

@@

@@

@@

haven & haven & 2.1.1 & 2019-07-04 & CRAN (R 3.6.0)\\

@@

hms & hms & 0.5.1 & 2019-08-23 & CRAN (R 3.6.0)\\

@@

htmlwidgets & htmlwidgets & 1.3 & 2018-09-30 & CRAN (R 3.6.0)\\

@@

@@

@@

jpeg & jpeg & 0.1-8 & 2014-01-23 & CRAN (R 3.6.0)\\

@@

kernlab & kernlab & 0.9-27 & 2018-08-10 & CRAN (R 3.6.0)\\
KernSmooth & KernSmooth & 2.23-15 & 2015-06-29 & CRAN (R 3.6.1)\\
knitr & knitr & 1.25 & 2019-09-18 & CRAN (R 3.6.1)\\

@@

@@

@@

maptools & maptools & 0.9-5 & 2019-02-18 & CRAN (R 3.6.0)\\

@@

@@

@@

nlme & nlme & 3.1-141 & 2019-08-01 & CRAN (R 3.6.0)\\

@@

patchwork & patchwork & 0.0.1 & 2019-10-03 & Github (thomasp85/patchwork@36b4918)\\

@@

pkgbuild & pkgbuild & 1.0.5 & 2019-08-26 & CRAN (R 3.6.0)\\

@@

@@

prodlim & prodlim & 2018.04.18 & 2018-04-18 & CRAN (R 3.6.0)\\

@@

purrr & purrr & 0.3.2 & 2019-03-15 & CRAN (R 3.6.0)\\
R6 & R6 & 2.4.0 & 2019-02-14 & CRAN (R 3.6.0)\\
Rcpp & Rcpp & 1.0.2 & 2019-07-25 & CRAN (R 3.6.0)\\

@@

rgdal & rgdal & 1.4-4 & 2019-05-29 & CRAN (R 3.6.0)\\
rgeos & rgeos & 0.5-1 & 2019-08-05 & CRAN (R 3.6.1)\\

@@

rlang & rlang & 0.4.0 & 2019-06-25 & CRAN (R 3.6.0)\\

@@

rmarkdown & rmarkdown & 1.16 & 2019-10-01 & CRAN (R 3.6.1)\\

@@

@@

rticles & rticles & 0.10 & 2019-08-21 & CRAN (R 3.6.0)\\

@@

rvest & rvest & 0.3.4 & 2019-05-15 & CRAN (R 3.6.0)\\
scales & scales & 1.0.0 & 2018-08-09 & CRAN (R 3.6.0)\\

@@

sp & sp & 1.3-1 & 2018-06-05 & CRAN (R 3.6.0)\\
spasm & spasm & 0.1.0.9000 & 2019-10-09 & local\\

@@

survival & survival & 2.44-1.1 & 2019-04-01 & CRAN (R 3.6.1)\\

@@

testthat & testthat & 2.2.1 & 2019-07-25 & CRAN (R 3.6.0)\\

@@

tinytex & tinytex & 0.16 & 2019-09-17 & CRAN (R 3.6.1)\\
units & units & 0.6-4 & 2019-08-22 & CRAN (R 3.6.0)\\

@@

xfun & xfun & 0.10 & 2019-10-01 & CRAN (R 3.6.1)\\

@@

@@

zeallot & zeallot & 0.1.0 & 2018-01-28 & CRAN (R 3.6.0)\\*

@@

\textasciitilde{}uniform(0.6,0.95)\strut

@@

\textasciitilde{}uniform(0,0.5 * P)\strut

@@

\textasciitilde{}uniform(0.01,1)\strut

@@

\textasciitilde{}uniform(0.01,4)\strut

@@

\textasciitilde{}uniform(0.1,1.25)\strut

@@

\textasciitilde{}round(uniform(5,0.66 * T))\strut

@@

\textasciitilde{}uniform(0.01,0.75)\strut

@@

@@

\begin{figure}
\centering
\includegraphics{figs/estimation-cartoon.png}
\caption{\label{fig:cartoon}Cartoon illustration of the hierarchichal difference-in-difference estimator}
\end{figure}

@@

@@

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Supporting Information: The Regional Effects of Marine Protected Areas},
            pdfauthor={Daniel Ovando,Jennifer E. Caselle,Christopher Costello,Olivier Deschenes,Steven D. Gaines,Ray Hilborn,Owen Liu},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx}
% grffile has become a legacy package: https://ctan.org/pkg/grffile
\IfFileExists{grffile.sty}{%
\usepackage{grffile}
}{}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

base64enc & base64enc & 0.1-3 & 2015-07-28 & CRAN (R 3.6.0)\\
bayesplot & bayesplot & 1.7.0 & 2019-05-23 & CRAN (R 3.6.0)\\

@@

bookdown & bookdown & 0.15 & 2019-11-12 & CRAN (R 3.6.0)\\
boot & boot & 1.3-23 & 2019-07-05 & CRAN (R 3.6.0)\\

@@

classInt & classInt & 0.4-2 & 2019-10-17 & CRAN (R 3.6.0)\\

@@

colourpicker & colourpicker & 1.0 & 2017-09-27 & CRAN (R 3.6.0)\\

@@

crosstalk & crosstalk & 1.0.0 & 2016-12-21 & CRAN (R 3.6.0)\\
crul & crul & 0.9.0 & 2019-11-06 & CRAN (R 3.6.0)\\

@@

data.table & data.table & 1.12.6 & 2019-10-18 & CRAN (R 3.6.0)\\

@@

devtools & devtools & 2.2.1 & 2019-09-24 & CRAN (R 3.6.0)\\
digest & digest & 0.6.23 & 2019-11-23 & CRAN (R 3.6.0)\\
doParallel & doParallel & 1.0.15 & 2019-08-02 & CRAN (R 3.6.0)\\

@@

DT & DT & 0.10 & 2019-11-12 & CRAN (R 3.6.0)\\
dygraphs & dygraphs & 1.1.1.6 & 2018-07-11 & CRAN (R 3.6.0)\\

@@

farver & farver & 2.0.1 & 2019-11-13 & CRAN (R 3.6.0)\\
fastmap & fastmap & 1.0.1 & 2019-10-08 & CRAN (R 3.6.0)\\
FishLife & FishLife & 2.0.0 & 2019-11-17 & Github (james-thorson/FishLife@3a6bdca)\\

@@

furrr & furrr & 0.1.0 & 2018-05-16 & CRAN (R 3.6.0)\\
future & future & 1.15.0 & 2019-11-08 & CRAN (R 3.6.0)\\
gdtools & gdtools & 0.2.1 & 2019-10-14 & CRAN (R 3.6.0)\\

@@

geojsonio & geojsonio & 0.8.0 & 2019-10-29 & CRAN (R 3.6.0)\\

@@

gganimate & gganimate & 1.0.4 & 2019-11-18 & CRAN (R 3.6.1)\\

@@

ggridges & ggridges & 0.5.1 & 2018-09-27 & CRAN (R 3.6.0)\\

@@

gh & gh & 1.0.1 & 2017-07-16 & CRAN (R 3.6.0)\\
gifski & gifski & 0.8.6 & 2018-09-28 & CRAN (R 3.6.0)\\
globals & globals & 0.12.4 & 2018-10-11 & CRAN (R 3.6.0)\\

@@

gtools & gtools & 3.8.1 & 2018-06-26 & CRAN (R 3.6.0)\\
haven & haven & 2.2.0 & 2019-11-08 & CRAN (R 3.6.0)\\

@@

hms & hms & 0.5.2 & 2019-10-30 & CRAN (R 3.6.0)\\

@@

htmlwidgets & htmlwidgets & 1.5.1 & 2019-10-08 & CRAN (R 3.6.0)\\

@@

httpuv & httpuv & 1.5.2 & 2019-09-11 & CRAN (R 3.6.0)\\

@@

igraph & igraph & 1.2.4.1 & 2019-04-22 & CRAN (R 3.6.0)\\
inline & inline & 0.3.15 & 2018-05-18 & CRAN (R 3.6.0)\\

@@

jpeg & jpeg & 0.1-8.1 & 2019-10-24 & CRAN (R 3.6.0)\\

@@

kernlab & kernlab & 0.9-29 & 2019-11-12 & CRAN (R 3.6.0)\\
KernSmooth & KernSmooth & 2.23-16 & 2019-10-15 & CRAN (R 3.6.0)\\
knitr & knitr & 1.26 & 2019-11-12 & CRAN (R 3.6.0)\\

@@

later & later & 1.0.0 & 2019-10-04 & CRAN (R 3.6.1)\\

@@

listenv & listenv & 0.7.0 & 2018-01-21 & CRAN (R 3.6.0)\\
lme4 & lme4 & 1.1-21 & 2019-03-05 & CRAN (R 3.6.0)\\
loo & loo & 2.1.0 & 2019-03-13 & CRAN (R 3.6.0)\\

@@

maptools & maptools & 0.9-8 & 2019-10-05 & CRAN (R 3.6.0)\\
markdown & markdown & 1.1 & 2019-08-07 & CRAN (R 3.6.0)\\

@@

matrixStats & matrixStats & 0.55.0 & 2019-09-07 & CRAN (R 3.6.0)\\

@@

mime & mime & 0.7 & 2019-06-11 & CRAN (R 3.6.0)\\
miniUI & miniUI & 0.1.1.1 & 2018-05-18 & CRAN (R 3.6.0)\\
minqa & minqa & 1.2.4 & 2014-10-09 & CRAN (R 3.6.0)\\

@@

ncdf4 & ncdf4 & 1.17 & 2019-10-23 & CRAN (R 3.6.0)\\
nlme & nlme & 3.1-142 & 2019-11-07 & CRAN (R 3.6.0)\\
nloptr & nloptr & 1.2.1 & 2018-10-03 & CRAN (R 3.6.0)\\

@@

patchwork & patchwork & 1.0.0 & 2019-12-01 & CRAN (R 3.6.1)\\

@@

pkgbuild & pkgbuild & 1.0.6 & 2019-10-09 & CRAN (R 3.6.0)\\

@@

plotROC & plotROC & 2.2.1 & 2018-06-23 & CRAN (R 3.6.0)\\

@@

prodlim & prodlim & 2019.11.13 & 2019-11-17 & CRAN (R 3.6.1)\\
progress & progress & 1.2.2 & 2019-05-16 & CRAN (R 3.6.0)\\
promises & promises & 1.1.0 & 2019-10-04 & CRAN (R 3.6.1)\\

@@

purrr & purrr & 0.3.3 & 2019-10-18 & CRAN (R 3.6.0)\\
R6 & R6 & 2.4.1 & 2019-11-12 & CRAN (R 3.6.0)\\
RANN & RANN & 2.6.1 & 2019-01-08 & CRAN (R 3.6.0)\\
Rcpp & Rcpp & 1.0.3 & 2019-11-08 & CRAN (R 3.6.0)\\
RcppRoll & RcppRoll & 0.3.0 & 2018-06-05 & CRAN (R 3.6.0)\\

@@

rfishbase & rfishbase & 3.0.4 & 2019-06-27 & CRAN (R 3.6.0)\\
rgdal & rgdal & 1.4-7 & 2019-10-28 & CRAN (R 3.6.0)\\
rgeos & rgeos & 0.5-2 & 2019-10-03 & CRAN (R 3.6.0)\\

@@

rlang & rlang & 0.4.2 & 2019-11-23 & CRAN (R 3.6.0)\\

@@

rmarkdown & rmarkdown & 1.17 & 2019-11-13 & CRAN (R 3.6.0)\\

@@

rsconnect & rsconnect & 0.8.15 & 2019-07-22 & CRAN (R 3.6.0)\\
rstan & rstan & 2.19.2 & 2019-07-09 & CRAN (R 3.6.0)\\
rstanarm & rstanarm & 2.19.2 & 2019-10-03 & CRAN (R 3.6.1)\\
rstantools & rstantools & 2.0.0 & 2019-09-15 & CRAN (R 3.6.0)\\

@@

rticles & rticles & 0.12 & 2019-11-12 & CRAN (R 3.6.0)\\

@@

rvest & rvest & 0.3.5 & 2019-11-08 & CRAN (R 3.6.0)\\
scales & scales & 1.1.0 & 2019-11-18 & CRAN (R 3.6.0)\\

@@

shiny & shiny & 1.4.0 & 2019-10-10 & CRAN (R 3.6.0)\\
shinyjs & shinyjs & 1.0 & 2018-01-08 & CRAN (R 3.6.0)\\
shinystan & shinystan & 2.5.0 & 2018-05-01 & CRAN (R 3.6.0)\\
shinythemes & shinythemes & 1.1.2 & 2018-11-06 & CRAN (R 3.6.0)\\
sp & sp & 1.3-2 & 2019-11-07 & CRAN (R 3.6.0)\\
spasm & spasm & 0.1.0.9000 & 2019-10-16 & local\\
StanHeaders & StanHeaders & 2.19.0 & 2019-09-07 & CRAN (R 3.6.0)\\

@@

survival & survival & 3.1-7 & 2019-11-09 & CRAN (R 3.6.0)\\

@@

testthat & testthat & 2.3.0 & 2019-11-05 & CRAN (R 3.6.0)\\
threejs & threejs & 0.3.1 & 2017-08-13 & CRAN (R 3.6.0)\\

@@

tinytex & tinytex & 0.17 & 2019-10-30 & CRAN (R 3.6.0)\\
TMB & TMB & 1.7.15 & 2018-11-09 & CRAN (R 3.6.0)\\
tweenr & tweenr & 1.0.1 & 2018-12-14 & CRAN (R 3.6.0)\\
units & units & 0.6-5 & 2019-10-08 & CRAN (R 3.6.0)\\

@@

xfun & xfun & 0.11 & 2019-11-12 & CRAN (R 3.6.0)\\

@@

xtable & xtable & 1.8-4 & 2019-04-21 & CRAN (R 3.6.0)\\
xts & xts & 0.11-2 & 2018-11-05 & CRAN (R 3.6.0)\\

@@

zeallot & zeallot & 0.1.0 & 2018-01-28 & CRAN (R 3.6.0)\\
zoo & zoo & 1.8-6 & 2019-05-28 & CRAN (R 3.6.0)\\*

@@

\textasciitilde uniform(0.6,0.95)\strut

@@

\textasciitilde uniform(0,0.5 * P)\strut

@@

\textasciitilde uniform(0.01,1)\strut

@@

\textasciitilde uniform(0.01,4)\strut

@@

\textasciitilde uniform(0.1,1.25)\strut

@@

\textasciitilde round(uniform(5,0.66 * T))\strut

@@

\textasciitilde uniform(0.01,0.75)\strut

@@

At the rawest level, the data are counts of finfish in 2cm length bins along a 30m x 2m transect at various sites and depths. These length bins are converted to biomass, and then biomass densities, by converting length to weights using available allometric data and dividing by the transect area. Our goal is to estimate the effect of the MPAs on these biomass densities of fish throughout the Channel Islands. We fit this model using a hierarchical mixed-effect framework using Template Model Builder (TMB, Kristensen et al. 2016) in R. The model consists of three levels, the first (starting from the ``bottom'') being transect-level densities of fish species observed by PISCO, which are standardized into a standardized biomass abundance index, accounting for both probability of detection and expected density as a result of changes in both abundance and covariates such as visibility and observer experience (see Maunder and Langley 2004). For the second stage, we break the abundance indices into targeted and non-targeted species (per the classifications in the PISCO data), and estimate the mean trend of each group (targeted and non-targeted) over time. In the third stage, we estimate the difference in the de-meaned trend between the targeted and non-targeted fishes (controlling for factors such as water temperature, kelp cover, and commercial fishery catches), that under the assumptions of the model reflects the causal effect of the MPAs on the outcome of interest (in this case regional biomass density of targeted fishes). All three of these steps are integrated into the same estimation model, in order to propagate uncertainty through the model correctly. Simpler versions of the estimation model, as well as a synthetic control identification strategy, were assessed as well and showed results consistent with the model in our main results.

@@

\newpage
\begin{figure}
\includegraphics[width=6in]{figs/estimation-cartoon} \caption{Cartoon illustration of the hierarchichal difference-in-difference estimator}\label{fig:cartoon}
\end{figure}

@@

\leavevmode\hypertarget{ref-kristensen2016}{}%
Kristensen, Kasper, Anders Nielsen, Casper W. Berg, Hans Skaug, and Bradley M. Bell. 2016. ``\textbf{TMB} : Automatic Differentiation and Laplace Approximation.'' \emph{Journal of Statistical Software} 70 (5). \url{https://doi.org/10.18637/jss.v070.i05}.

@@

\leavevmode\hypertarget{ref-maunder2004}{}%
Maunder, Mark N., and Adam D. Langley. 2004. ``Integrating the Standardization of Catch-Per-Unit-of-Effort into Stock Assessment Models: Testing a Population Dynamics Model and Using Multiple Data Types.'' \emph{Fisheries Research}, Models in Fisheries Research: GLMs, GAMS and GLMMs, 70 (23): 389--95. \url{https://doi.org/10.1016/j.fishres.2004.08.015}.
